Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-16 Documentation/manuscript.tex
Paper edits in Manuscript.RNW

\begin{document}

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are so named because of the way in which they are implemented. Instead of giving participants one large survey, researchers will create multiple “forms”, each containing only a subset of the full survey’s questions. A common setup is the three-form design \citep{graham1996maximizing}. In the three-form design the full survey is split into four blocks, X, A, B, and C. Each form of the survey includes the X block as well as two of the other three blocks. This leaves us with the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. We note that every block is paired together in at least one of the forms. By designing our forms in this manner we are able to estimate the relationship between any given items regardless of which blocks they are in. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows us to do that. \par

@@

<<echo = FALSE>>=
# Creating dataframe to visualize - one subject's questions for 5 days
split.form <- function(set, nrem = 2, bound = 0){

set[set$Day >= bound, paste0("Q",1:8)] <- t(apply(set[set$Day >= bound,paste0("Q",1:8)], 1, function(x){
    ind <- sample(1:8, nrem)
    x[ind] <- NA
    as.numeric(x)
  }))

  return(set)

}
@

<<echo = FALSE>>=
wave.des <- function(set, nmiss, ...) { # nmiss is the number of days each person would miss? 11?? Like, miss a fourth of the days?
  id <- sample(2:45, size=nmiss)
  for (i in 1:nmiss) {
    set[set$Day %in% id[i], c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')] <- NA
  }
  return(set)
}
@

<<warning=FALSE, echo = FALSE>>=
cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
fill <- matrix(1, 45, 8)
dat <- data.frame(fill)
colnames(dat) <- cols
dat$Day <- seq.int(nrow(dat))
set.seed(1234)
split.dat <- split.form(dat)[1:8]
#split.dat
@

<<warning=FALSE,message=FALSE,echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- split.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")

  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
@

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
splitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
@

<<warning=FALSE,echo=FALSE>>=
cols <- c('Q1','Q2','Q3','Q4','Q5','Q6','Q7','Q8')
fill <- matrix(1, 45, 8)
dat <- data.frame(fill)
colnames(dat) <- cols
dat$Day <- seq.int(nrow(dat))
set.seed(1234)
alternate.split.dat <- split.form(dat, bound = 3)[1:8]
#alternate.split.dat
@

<<warning=FALSE,message=FALSE,echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- alternate.split.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")

  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
@

<<warning=FALSE,echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
alternatesplitplot <- ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")

#+ geom_vline(xintercept=seq(1.5, 7.5, 2), lwd=1, colour="white") + geom_hline(yintercept=seq(1.5, 4.5, 1), lwd=1, colour="white")
@

<<echo=FALSE>>=
set.seed(1234)
wave.dat <- wave.des(dat,11)
#wave.dat
@

<<echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(reshape2)
datmelt <- wave.dat[1:8] %>% is.na %>% melt
colnames(datmelt) <- c("Day","Question","Missing")
#datmelt$block <- ifelse((datmelt$Question=="Q1")|(datmelt$Question=="Q8"),"X",ifelse((datmelt$Question=="Q2")|(datmelt$Question=="Q3"),"A",ifelse((datmelt$Question=="Q4")|(datmelt$Question=="Q5"),"B",ifelse((datmelt$Question=="Q6")|(datmelt$Question=="Q7"),"C",0))))
datmelt$color <- ifelse(datmelt$Missing == "TRUE", "Missing", "Observed")

  #ifelse(datmelt$Missing == "TRUE", "Missing", ifelse(datmelt$block == "X","X",ifelse(datmelt$block == "A","A",ifelse(datmelt$block == "B","B",ifelse(datmelt$block == "C","C","Missing")))))
@

<<echo=FALSE>>=
cols <- c("Missing" = "red", "Observed" = "skyblue3")
waveplot <-  ggplot(datmelt, aes(Question, Day, fill=color)) + geom_raster() + scale_fill_manual(values = cols)  + theme(axis.text.x = element_text(angle=45, vjust=0.5),panel.background = element_rect(fill = NA)) + labs(x = "Questions Asked",y = "Day",fill="Block") + scale_y_reverse() + theme(legend.title=element_blank(),legend.position="none")
@

<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE>>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

\subsection{Simulations}
\label{sec:2.2}
The first step in the process of creating our simulated datasets was to use the data from \citet{pellowski2016alcohol} and obtain parameter estimates to quantify the relationships between variables. We then treated these estimated relationships as the “true” relationships and drew two-hundred samples using these parameters. While we would have liked to simulate a larger number of samples we were limited by computational ability. Our purpose in simulating these datasets was to see how well they would be able to capture the true relationship between medication adherence on a certain day, whether or not a participant drank that day, and their beliefs about alcohol-medication interactivity (included as a Z-transformed test score). Specifically, our model of interest is the random intercept model with time effect found below: \\

@@

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation we took the format of the original data, which included sixty participants, and expanded it to include one-hundred and twenty. The rest of the simulation process was carried out as before. We noted earlier that cost savings created from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, then researchers can design missingness in whichever method is most convenient. We further note, that because Wave Missingness allows for greater savings an increase in sample size is more reasonable for that type of Missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering “yes” on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. If researchers have a questionnaire where they do not expect any of the answers to be obviously related the results here may help to choose which missingness design would be most optimal. \par
\subsubsection{High Time Effect}
In this final scenario we hoped to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively. We note that instead of increasing the value of $\beta_3$, the slope for time effect, we decreased all the other parameters. We did this because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. By decreasing the other variables effects we were able to ensure that time has a disproportionate effect without incurring this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

@@

<<>>=
load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high.RData")
high <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med.RData")
med <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_high_hightime1.RData")
high <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_med_hightime1.RData")
med <- d

load("~/Dropbox/designedMissingnessGit/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)

@

% latex table generated in R 3.5.0 by xtable 1.8-2 package
% Mon May 14 21:02:34 2018
\begin{table}[ht]
\centering
\begin{tabular}{lllrrrr}
  \hline
Design & \% Missingness  & Parameter & Coverage & Bias & MSE & FMI \\ 
  \hline
 &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
   \hline
   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
   \hline
   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
   \hline
   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
   \hline
   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
   \hline
   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
   \hline
   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
   \hline
   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
   \hline
   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[b!]
	\centering
	\caption{Results of Analysis before imposing Missingness in each Scenario}
	\setlength{\tabcolsep}{0.1cm}
	\label{tab:table2}
	\begin{tabular}{cc|ccccc}
		\toprule
		Scenario & Parameter & Bias & Percent Bias & MSE & Coverage & CI Length \\
		\midrule
		\multirow{4}{*}{\parbox{2cm}{Primary \\ Analysis (N=60)}} 
		& $\gamma_0$ & 0.151 & 6.55\% & 0.037 & 99.0\% & 0.750 \\
		& $\beta_1$ & 0.133 & 23.75\% & 0.028 & 95.5\% & 0.652 \\
		& $\beta_2$ & 0.120 & 9.40\% & 0.022 & 97.5\% & 0.610 \\
		& $\beta_3$ & 0.007 & 3.42\% & 7.11$*10^-5$ & 97.0\% & 0.034 \\
		\midrule
		\midrule
		\multirow{4}{*}{\parbox{2cm}{Increased \\ Sample (N=120)}} 
		& $\gamma_0$ & 0.106 & 4.61\% & 0.018 & 98.0\% & 0.528 \\
		& $\beta_1$ & 0.099 & 17.63\% & 0.016 & 93.0\% & 0.460 \\
		& $\beta_2$ & 0.091 & 7.12\% & 0.013 & 95.5\% & 0.429 \\
		& $\beta_3$ & 0.005 & 2.34\% & 3.52$*10^-5$ & 96.5\% & 0.024 \\
		\midrule
		\midrule
		\multirow{4}{*}{\parbox{2cm}{Low \\Inter-Survey Correlation (N=60)}} 
		& $\gamma_0$ & 0.145 & 6.29\% & 0.033 & 99.0\% & 0.747 \\
		& $\beta_1$ & 0.130 & 23.27\% & 0.027 & 94.5\% & 0.651 \\
		& $\beta_2$ & 0.126 & 9.83\% & 0.026 & 94.0\% & 0.611 \\
		& $\beta_3$ & 0.007 & 3.69\% & 8.88$*10^-5$ & 93.0\% & 0.034 \\
		\midrule
		\midrule
		\multirow{4}{*}{\parbox{2cm}{High \\Time Effect (N=60)}}
		& $\gamma_0$ & 0.170 & 3.69\% & 0.045 & 98.5\% & 0.888 \\
		& $\beta_1$ & 0.123 & 43.86\% & 0.024 & 96.0\% & 0.598 \\
		& $\beta_2$ & 0.124 & 19.35\% & 0.025 & 93.5\% & 0.575 \\
		& $\beta_3$ & 0.006 & 2.95\% & 5.50$*10^-5$ & 95.5\% & 0.030 \\
		\bottomrule
	\end{tabular}
\end{table}

Of note in the complete-data primary analysis is that the coverage of our 95\% CIs is larger than expected for our parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, we should keep this in mind when analyzing our results from the PM designs provided in Table \ref{tab:table3}. In Table \ref{tab:table3} as in Tables \ref{tab:table4}, \ref{tab:table5}, and \ref{tab:table6} bold values indicate "Unacceptable" results. That is, a Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.

\begin{table}[p]
	\centering
	\caption{Primary Simulation Results (N=60)}
	\setlength{\tabcolsep}{0.1cm}
	\label{tab:table3}
	\hspace*{-1cm}
	\begin{tabular}{c|c|c|cccccc}
		\toprule
		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
		\midrule
		\multirow{12}{*}{Split Form}
		& \multirow{4}{*}{Low(25\%)}
		& $\gamma_0$ & 0.151 & 6.59\% & 0.037 & 99.5\% & 0.753 & 0.009 \\
		&& $\beta_1$ & 0.139 & 24.78\% & 0.029 & 96.0\% & 0.693 & 0.112 \\
		&& $\beta_2$ & 0.120 & 9.41\% & 0.022 & 97.0\% & 0.610 & 0.002 \\
		&& $\beta_3$ & 0.007 & 3.42\% & 7.12$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(50\%)}
		& $\gamma_0$ & 0.153 & 6.67\% & 0.037 & 99.0\% & 0.765 & 0.040 \\
		&& $\beta_1$ & 0.162 & 28.93\% & 0.041 & 95.5\% & 0.869 & 0.390 \\
		&& $\beta_2$ & 0.121 & 9.51\% & 0.022 & 97.0\% & 0.616 & 0.007 \\
		&& $\beta_3$ & 0.007 & 3.40\% & 6.99$*10^-5$ & 98.5\% & 0.034 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(75\%)}
		& $\gamma_0$ & 0.154 & 6.70\% & 0.039 & 98.5\% & 0.818 & 0.147 \\
		&& $\beta_1$ & \textbf{0.225} & \textbf{40.16}\% & \textbf{0.076} & 97.5\% & 1.464 & 0.710 \\
		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 97.5\% & 0.611 & 0.022 \\
		&& $\beta_3$ & 0.007 & 3.42\% & 7.02$*10^-5$ & 98.0\% & 0.035 & 0.032 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
		& \multirow{4}{*}{Low(23.9\%)}
		& $\gamma_0$ & 0.151 & 6.57\% & 0.037 & 98.0\% & 0.753 & 0.008 \\
		&& $\beta_1$ & 0.137 & 24.55\% & 0.030 & 96.0\% & 0.690 & 0.105 \\
		&& $\beta_2$ & 0.120 & 9.39\% & 0.022 & 97.5\% & 0.611 & 0.002 \\
		&& $\beta_3$ & 0.007 & 3.42\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.003 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(47.8\%)}
		& $\gamma_0$ & 0.153 & 6.67\% & 0.038 & 99.5\% & 0.760 & 0.030 \\
		&& $\beta_1$ & 0.151 & 26.93\% & 0.036 & 96.0\% & 0.811 & 0.324 \\
		&& $\beta_2$ & 0.119 & 9.28\% & 0.022 & 96.0\% & 0.611 & 0.006 \\
		&& $\beta_3$ & 0.007 & 3.44\% & 7.10$*10^-5$ & 98.0\% & 0.034 & 0.007 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(71.7\%)}
		& $\gamma_0$ & 0.164 & 7.13\% & 0.042 & 98.0\% & 0.799 & 0.105 \\
		&& $\beta_1$ & \textbf{0.225} & \textbf{40.14\%} & \textbf{0.080} & 96.0\% & 1.265 & 0.640 \\
		&& $\beta_2$ & 0.117 & 9.13\% & 0.021 & 97.5\% & 0.615 & 0.019 \\
		&& $\beta_3$ & 0.007 & 3.46\% & 7.07$*10^-5$ & 98.0\% & 0.034 & 0.023 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
		& \multirow{4}{*}{Low(24.4\%)}
		& $\gamma_0$ & 0.152 & 6.61\% & 0.037 & 99.5\% & 0.757 & 0.023 \\
		&& $\beta_1$ & 0.147 & 26.25\% & 0.033 & 96.0\% & 0.767 & 0.270 \\
		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 96.0\% & 0.610 & 0.004 \\
		&& $\beta_3$ & 0.007 & 3.41\% & 6.97$*10^-5$ & 98.0\% & 0.034 & 0.006 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(48.9\%)}
		& $\gamma_0$ & 0.157 & 6.84\% & 0.039 & 100.0\% & 0.767 & 0.052 \\
		&& $\beta_1$ & \textbf{0.190} & \textbf{33.95\%} & \textbf{0.058} & 94.5\% & 0.934 & 0.465 \\
		&& $\beta_2$ & 0.119 & 9.27\% & 0.021 & 97.5\% & 0.609 & 0.008 \\
		&& $\beta_3$ & 0.007 & 3.34\% & 6.80$*10^-5$ & 98.0\% & 0.034 & 0.010 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(73.3\%)}
		& $\gamma_0$ & 0.168 & 7.30\% & 0.045 & 99.5\% & 0.807 & 0.129 \\
		&& $\beta_1$ & \textbf{0.290} & \textbf{51.77\%} & \textbf{0.132} & \textbf{88.5\%} & 1.335 & 0.680 \\
		&& $\beta_2$ & 0.119 & 9.32\% & 0.022 & 96.0\% & 0.614 & 0.017 \\
		&& $\beta_3$ & 0.007 & 3.40\% & 6.96$*10^-5$ & 98.5\% & 0.034 & 0.025 \\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table}[p]
	\centering
	\caption{Increased Sample Size simulation Results (N=120)}
	\setlength{\tabcolsep}{0.1cm}
	\label{tab:table4}
	\hspace*{-1cm}
	\begin{tabular}{c|c|c|cccccc}
		\toprule
		Design & \% Missingness & Parameter & Bias & \% Bias & MSE & Coverage & CI Length & FMI \\
		\midrule
		\multirow{12}{*}{Split Form}
		& \multirow{4}{*}{Low(25\%)}
		& $\gamma_0$ & 0.106 & 4.60\% & 0.017 & 98.5\% & 0.533 & 0.022 \\
		&& $\beta_1$ & 0.106 & 18.96\% & 0.018 & 96.0\% & 0.548 & 0.263 \\
		&& $\beta_2$ & 0.091 & 7.14\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
		&& $\beta_3$ & 0.005 & 2.33\% & 3.47$*10^-5$ & 96.5\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(50\%)}
		& $\gamma_0$ & 0.112 & 4.85\% & 0.019 & 98.0\% & 0.542 & 0.057 \\
		&& $\beta_1$ & 0.134 & 23.86\% & \textbf{0.027} & 95.0\% & 0.696 & 0.489 \\
		&& $\beta_2$ & 0.092 & 7.15\% & 0.013 & 96.5\% & 0.430 & 0.009 \\
		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(75\%)}
		& $\gamma_0$ & 0.110 & 4.80\% & 0.019 & 99.5\% & 0.575 & 0.153 \\
		&& $\beta_1$ & \textbf{0.194} & \textbf{34.59\%} & \textbf{0.057} & 94.5\% & 1.088 & 0.742 \\
		&& $\beta_2$ & 0.092 & 7.20\% & 0.013 & 95.0\% & 0.432 & 0.021 \\
		&& $\beta_3$ & 0.005 & 2.31\% & 3.42$*10^-5$ & 97.5\% & 0.024 & 0.026 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Altered \\ Split Form}}
		& \multirow{4}{*}{Low(23.9\%)}
		& $\gamma_0$ & 0.107 & 4.64\% & 0.017 & 98.0\% & 0.533 & 0.022 \\
		&& $\beta_1$ & 0.111 & 19.80\% & 0.020 & 94.5\% & 0.545 & 0.263 \\
		&& $\beta_2$ & 0.091 & 7.08\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
		&& $\beta_3$ & 0.005 & 2.31\% & 3.46$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(47.8\%)}
		& $\gamma_0$ & 0.115 & 4.99\% & 0.020 & 98.0\% & 0.542 & 0.056 \\
		&& $\beta_1$ & 0.138 & 24.65\% & \textbf{0.028} & 94.5\% & 0.693 & 0.494 \\
		&& $\beta_2$ & 0.091 & 7.24\% & 0.013 & 96.0\% & 0.430 & 0.008 \\
		&& $\beta_3$ & 0.005 & 2.34\% & 3.54$*10^-5$ & 96.0\% & 0.024 & 0.011 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(71.7\%)}
		& $\gamma_0$ & 0.115 & 5.01\% & 0.020 & 99.0\% & 0.563 & 0.119 \\
		&& $\beta_1$ & \textbf{0.188} & \textbf{33.65\%} & \textbf{0.058} & 91.5\% & 0.958 & 0.681 \\
		&& $\beta_2$ & 0.092 & 7.16\% & 0.013 & 96.0\% & 0.432 & 0.018 \\
		&& $\beta_3$ & 0.005 & 2.30\% & 3.44$*10^-5$ & 96.0\% & 0.024 & 0.020 \\
		\midrule
		\midrule
		\multirow{12}{*}{\parbox{1.75cm}{Wave \\ Missingness}}
		& \multirow{4}{*}{Low(24.4\%)}
		& $\gamma_0$ & 0.108 & 4.72\% & 0.018 & 98.0\% & 0.533 & 0.024 \\
		&& $\beta_1$ & 0.123 & 21.90\% & \textbf{0.024} & 92.0\% & 0.551 & 0.287 \\
		&& $\beta_2$ & 0.092 & 7.18\% & 0.013 & 96.0\% & 0.429 & 0.004 \\
		&& $\beta_3$ & 0.005 & 2.35\% & 3.51$*10^-5$ & 96.0\% & 0.024 & 0.005 \\ \cline{2-9} \noalign{\smallskip}
		&\multirow{4}{*}{Medium(48.9\%)}
		& $\gamma_0$ & 0.111 & 4.84\% & 0.019 & 99.0\% & 0.540 & 0.052 \\
		&& $\beta_1$ & \textbf{0.168} & \textbf{30.02\%} & \textbf{0.043} & \textbf{85.5\%} & 0.671 & 0.489 \\
		&& $\beta_2$ & 0.092 & 7.22\% & 0.013 & 95.0\% & 0.429 & 0.007 \\
		&& $\beta_3$ & 0.005 & 2.32\% & 3.42$*10^-5$ & 97.0\% & 0.024 & 0.009 \\ \cline{2-9} \noalign{\smallskip}
		& \multirow{4}{*}{High(73.3\%)}
		& $\gamma_0$ & 0.123 & 5.33\% & 0.023 & 99.0\% & 0.558 & 0.108 \\
		&& $\beta_1$ & \textbf{0.248} & \textbf{44.26\%} & \textbf{0.099} & \textbf{82.0\%} & 0.894 & 0.666 \\
		&& $\beta_2$ & 0.094 & 7.36\% & 0.014 & 96.0\% & 0.430 & 0.013 \\

>>>>

\usepackage{Sweave}
\begin{document}
\input{manuscript-concordance}

@@

NA

@@

@@

\subsection{Simulations}
\label{sec:2.2}
NA

@@

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation we took the format of the original data, which included sixty participants, and expanded it to include one-hundred and twenty. The rest of the simulation process was carried out as before. We noted earlier that cost savings created from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, then researchers can design missingness in whichever method is most convenient. We further note, that because Wave Missingness allows for greater savings an increase in sample size is more reasonable for that type of Missingness. \par
\subsubsection{Low Inter-Survey Correlation}
NA
\subsubsection{High Time Effect}
In this final scenario we hoped to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this we changed the value of the parameters $\gamma_0, \beta_1, \beta_2,$ and $\beta_3$ to -4.6, 0.28, 0.64, and 0.2 respectively. We note that instead of increasing the value of $\beta_3$, the slope for time effect, we decreased all the other parameters. We did this because $\beta_3$ was already fairly large and increasing its value further would cause the probability of missing a dose to rapidly approach 1. By decreasing the other variables effects we were able to ensure that time has a disproportionate effect without incurring this problem. The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

@@

\begin{Schunk}
\begin{Sinput}
> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_high.RData")
> high <- d
> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_med.RData")
> med <- d
> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_low.RData")
> low <- d
> library(xtable)
> print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)
\end{Sinput}
\begin{Soutput}
% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Wed May 16 16:26:28 2018
\begin{table}[ht]
\centering
\begin{tabular}{lllrrrr}
  \hline
"" & "" & "" & Coverage & Bias & MSE & FMI \\ 
  \hline
 &  &  & 0.989 & 0.042 & 0.018 & 0.002 \\ 
   &  &  & 0.984 & -0.125 & 0.731 & 0.270 \\ 
   &  &  & 0.934 & 0.008 & 0.024 & 0.000 \\ 
   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
   &  &  & 0.986 & 0.040 & 0.019 & 0.012 \\ 
   &  &  & 0.993 & -0.168 & 0.750 & 0.557 \\ 
   &  &  & 0.932 & 0.008 & 0.024 & 0.002 \\ 
   &  &  & 0.940 & -0.000 & 0.000 & 0.008 \\ 
   &  &  & 0.984 & 0.036 & 0.027 & 0.030 \\ 
   &  &  & 0.991 & -0.713 & 9.933 & 0.625 \\ 
   &  &  & 0.932 & 0.009 & 0.027 & 0.005 \\ 
   &  &  & 0.939 & -0.000 & 0.000 & 0.021 \\ 
   &  &  & 0.988 & 0.042 & 0.018 & 0.002 \\ 
   &  &  & 0.977 & -0.114 & 0.696 & 0.250 \\ 
   &  &  & 0.933 & 0.008 & 0.024 & 0.000 \\ 
   &  &  & 0.943 & -0.000 & 0.000 & 0.001 \\ 
   &  &  & 0.988 & 0.040 & 0.018 & 0.010 \\ 
   &  &  & 0.994 & -0.167 & 0.782 & 0.549 \\ 
   &  &  & 0.931 & 0.009 & 0.024 & 0.002 \\ 
   &  &  & 0.944 & -0.000 & 0.000 & 0.006 \\ 
   &  &  & 0.983 & 0.036 & 0.022 & 0.027 \\ 
   &  &  & 0.990 & -0.686 & 10.509 & 0.665 \\ 
   &  &  & 0.928 & 0.009 & 0.026 & 0.007 \\ 
   &  &  & 0.946 & -0.000 & 0.000 & 0.023 \\ 
   &  &  & 0.991 & 0.040 & 0.018 & 0.006 \\ 
   &  &  & 0.998 & -0.116 & 0.545 & 0.458 \\ 
   &  &  & 0.932 & 0.008 & 0.024 & 0.001 \\ 
   &  &  & 0.941 & -0.000 & 0.000 & 0.003 \\ 
   &  &  & 0.991 & 0.029 & 0.018 & 0.055 \\ 
   &  &  & 0.988 & -0.112 & 0.345 & 0.752 \\ 
   &  &  & 0.934 & 0.009 & 0.024 & 0.007 \\ 
   &  &  & 0.951 & -0.000 & 0.000 & 0.032 \\ 
   &  &  & 0.994 & -0.003 & 0.022 & 0.258 \\ 
   &  &  & 0.988 & -0.105 & 0.284 & 0.903 \\ 
   &  &  & 0.937 & 0.011 & 0.025 & 0.039 \\ 
   &  &  & 0.960 & -0.000 & 0.000 & 0.175 \\ 
   \hline
\end{tabular}
\end{table}
\end{Soutput}
\begin{Sinput}
> load("C:/Users/Josie/Documents/GitHub/designedmissingness/Results/tables20180509_60_1_high_hightime1.RData")
